Collision rates of planetesimals near mean-motion resonances

### 2021-02-24 main.tex
Fix space around changa citation, prevent footnote text from splitting between pages

@@

To further elucidate this subject, we use the tree based N-body code {\sc ChaNGa}\citep{2008IEEEpds...ChaNGa, 2015AphCom..2..1}  to follow the 
collisional evolution of a planetesimal disc under the gravitational influence of a Jupiter-sized body. Because particle positions are sorted into a tree 
structure, neighbor finding and collision detection can be done quickly and efficiently. This considerably relaxes the constraints on resolution and 
integration time. With this toolset, we explore the collision rate structure of a planetesimal disc in the vicinity of mean-motion resonances with a planet. In 
particular, we would like to determine (1) what dynamics govern the collision rate profile near MMRs, (2) whether MMRs leave a detectable signature in the
collisionally-generated dust, and (3) whether these signatures can be used to determine or constrain the orbital properties of the perturbing planet.

>>>>

% Prevent footnotes from breaking across multiple pages
\interfootnotelinepenalty=10000

@@

To further elucidate this subject, we use the tree based N-body code {\sc ChaNGa} \citep{2008IEEEpds...ChaNGa, 2015AphCom..2..1} to follow the 
collisional evolution of a planetesimal disc under the gravitational influence of a Jupiter-sized body. Because particle positions are sorted into a tree 
structure, neighbor finding and collision detection can be done quickly and efficiently. This considerably relaxes the constraints on resolution and 
integration time. With this toolset, we explore the collision rate structure of a planetesimal disc in the vicinity of mean-motion resonances with a planet. In 
particular, we would like to determine (1) what dynamics govern the collision rate profile near MMRs, (2) whether MMRs leave a detectable signature in the
collisionally-generated dust, and (3) whether these signatures can be used to determine or constrain the orbital properties of the perturbing planet.
